\thetitle

### 2024-11-05 paper/paper.tex
Paper draft

Luminosity distance, $D_L$, is the appearant distance of an object based on the
measured luminosity. This does not take into any movement of the observed
object between the time when the light was emitted and the light is observed.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the relative
brightness. Magnitude is defined on a logarithmic scale where magnitude 1 has
100 times the brightness of magnitude 6. To convert magnitude to relative brightness, we use:

\begin{equation}
  a
\end{equation}

\begin{equation}
\label{eq:g_def}
  G = \sqrt{ \bigg( s_i + \frac{s_j p_j}{p_i} \bigg)
             \bigg( s_j + \frac{s_i p_i}{p_j} \bigg)
           }
    = \frac{s_i p_i + s_j p_j}{\sqrt{p_i p_j}}.
\end{equation}

@@

\section{Discussion of discrepancy}

\section{Conclusions}
What the heck?

>>>>

Luminosity distance, $D_L$, is the appearant distance of an object based on the
measured luminosity. This does not take into account any movement of the
observed object between the time when the light was emitted and the light is
observed.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the relative
brightness. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has
100 times the brightness of magnitude 6. To convert magnitude to relative
brightness $B$, we use

\begin{equation}
  B = \frac{1}{\sqrt[5]{100}^{M - 1}}.
\end{equation}

This is proportional to the amount of energy detected by a telescope. However,
we instead want a number that is proportional to the number of photons detected
by the telescope. Redshifting decreases the amount of energy carried by a
photon from $E_{\text{emit}}$ to $E_{\text{obs}}$, but we can correct for this
phenomenon by taking

\begin{equation}
  B^{*} = B \frac{E_{\text{emit}}}{E_{\text{obs}}}.
\end{equation}

Since the energy for a photon is given by $E = \frac{hc}{\lambda}$ where $h$ is
the Planck constant and $c$ is the speed of light, we have

\begin{equation}
\begin{aligned}
  B^{*} &= B \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
        &= B \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
\end{aligned}
\end{equation}

We use the redshift equation $(1 + z)\lambda_{\text{emit}} =
\lambda_{\text{obs}}$ to obtain

\begin{equation}
\begin{aligned}
  B^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
        &= B(1 + z).
\end{aligned}
\end{equation}

We note that since all Type Ia supernova have approximately the same intrinsic
brightness, we can use a geometric model to compute relative distances. Imagine
holding up two coins, one in each hand.  If you arange them so that the
distance from your eyes to the first coin double the distance from your eyes to
the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
More formally, for two objects of the same radius $r$, the appearant area $A$
is

\begin{equation}
  A = \pi \bigg(\frac{r}{d}\bigg)^2
\end{equation}

where $d$ is the relative distance between the two objects.

Replacing the area with the brightness, we have

\begin{equation}
\begin{aligned}
  B^{*} = \pi \bigg(\frac{r}{d}\bigg)^2 \\
      d = r \sqrt{\frac{\pi}{B^*}}.
\end{aligned}
\end{equation}

Finally, since this equation has no specified units, we will need to find a calibration factor $k$. To beautify the equation, we can collect all constants (which includes $r$ since all Type Ia supernova have the same intrinsic brightness) into $k$. This gives

\begin{equation}
\begin{aligned}
  d &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
    &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
\end{aligned}
\end{equation}

The results of this model are shown in Figure \ref{fig:corrected_uncalibrated}.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the corrected $B^*$ values for
  brightness.}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the uncorrected $B$ values for brightness.
  The deviation from linearity suggests that distant objects are
  farther away than expected due to an accelerated expansion rate.}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

It's worth noting that previous studies use $B$ instead of $B*$. According to
\citet{betoule2014},

\begin{displayquote}
  Specifically, the distance estimator used in this analysis (and in most
  similar cosmological analyses) assumes that supernovae with identical color,
  shape and galactic environment have on average the same intrinsic luminosity
  for all redshifts.
\end{displayquote}

This leads to

\begin{equation}
  d_{\text{uncorrected}} = k 10^\frac{M}{5}
\end{equation}

which is displayed in Figure \ref{fig:uncorrected_uncalibrated}.

@@

Calibrating a distance model involves finding a linear regression line for a
model and then computing the value $k$ required to make the regression model
match a Hubble paramater. By arbitrary choice, we use $H_0 = 70 \frac{km/s}{Mpsc}$.

The final units for distance will be in megaparsecs $Mpsc$. To find the
recessional speed for a given redshift, we use $v = cz$ where $c$ is the speed
of light.

To compute a model, we use non-parametric regression via repeated means as described in
\citet{siegel1982}. A comparison of both models is shown in Figure \ref{fig:calibrated}.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
  \caption{Calibrated distance model using both the corrected $B^*$ values as
  well as the uncorrected $B$ brightness values.}
  \label{fig:calibrated}
\end{figure}

\section{Next steps}
\label{sec:nextsteps}

Is my understanding of the literature correct? My understanding is that
existing models don't correct for the impact of redshift on the brightness of
distant objects, and models that use an accelerating expansion for the universe
are based on adding that correction back into the model.
